Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2023-05-18 docs/manuscript/manuscript.tex

\begin{abstract}
While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility, the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have kept geographers from conducting more reproduction studies.
This study addresses each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
We find ...
CONClUSION...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducibility is important for geographic research for the same reason it is important in other areas of research. 
In principle, reproducible research publicly discloses the evidence used to support claims made in prior work which facilitates the independent verification of those claims and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009} .
While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
Nonetheless, research across disciplines suggests that the results of many studies cannot be independently recreated \citep[see][]{moraila2014measuring, chang2015economics, open2015estimating, iqbal2016reproducible} and that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
The available evidence links the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details of to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
At the same time a sizable portion of the researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.

Although not yet systematically measured, many of these same factors may be impacting the reproducibility of geographic research.
The small number of reproduction studies available within the discipline suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep[see][]{ Kedron2021ssrn, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
The available surveys of research practices in the discipline also support this conclusion as few researchers report sharing their data, metadata, or source code \citep{balz2020reproducibility, konkol2019, ostermann2017}.
At the same time, recent reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.

Despite these suggestive findings, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
This knowledge gap exists because researchers conducting reproducibility assessments have not defined clear target populations or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}. 
Attempted reproductions of geographic research for example focus on the computational reproducibility of conference papers \citep{Nust-AGILE_2018} or specific topics such as COVID-19 \citep{Holler2023disability,kedron2021GA, paez2022reproducibility}.

More broadly, attempts to catalog or survey reproducible research practices have drawn data non-randomly from conveniently accessible archives such as conference paper series, specific journals, and disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2018empirical, stodden2018enabling}, or from self-selecting populations such as authors in specific journals, members of professional associations, and conference attendees \citep{baker20161} that are not necessarily representative of researchers active in a particular field. 
Like attempts to reproduce specific studies, reproducibility surveys also focus on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use. 
The few available surveys of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017} face these same challenges.

While geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}, we have yet to systematically assess the use of reproducible research practices across the discipline's diverse research traditions, or identify the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies. 
Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducibile research using a probability sampling scheme designed to capture the breadth of geographic research.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey first focusing on researcher perceptions and use of reproducible research practices, then analyzing researcher experiences attempting to reproduce prior work. 
We then discuss the implications of our survey results. 
Finally, we conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here. 
Excluding data that could be used to identify participants, all of the materials, methods, and code used to conduct and analyze our survey are available in online repositories with persistent links and identifiers. 
We encourage interested readers to critically evaluate and build on these materials through their own work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

\subsection*{Survey Instrument}
The survey consisted of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reproducibility, and (iv) experience conducting independent reproductions. 
Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
All researchers were presented questions about their definition of reproducibility, familiarity with and use of reproducible practices, and perceptions of barriers to reproducibility. 
A subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.

We pilot tested the survey instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

Participation in the survey was entirely voluntary. 
Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
Participants were also given the option to enter a random prize draw. 
The total possible compensation a participant was eligible to receive was 90 US dollars, awarded as a prepaid credit card.
Three prize winners were selected at random from those electing to enter the prize draw at the end of the data collection period.

The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
Each question on the survey was presented as a unique page. 
Adaptive questioning, conditionally displaying items based on responses to other items, was used to reduce the number of complexity of questions.
Participating researchers had the option to exit and re-enter the survey and were also able to review and/or change their answers using a back button as they progressed through the survey.

At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
Responses were downloaded from Qualtrics, anonymized, and stored in a password-protected databases.
We used a unique key to link this data with participant information (e.g., citation history) stored in a separate database during our statistical analyses. 
To preserve participant privacy that connection was severed at the end of our analysis.
We have only shared the anonymized response file through our public repository. 
As a result some of the result presented below cannot be directly replicated. 
We have indicated throughout our results section which analysis can and cannot be replicated using the data files and code share through our public repository.

@@

%%%%%%%%%%%
\subsubsection*{Statistical Approach}
We conduct two statistical analyses of the survey response.
First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.
Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years.
That analysis identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
Given the topical and epistemological variation that exists among geographic researchers, we examined differences by disciplinary subfield and methodological approach as part of each analysis.

%%%%%%%%%%%
\subsubsection*{Variable Construction}
For our first analysis, we constructed summary measures that aggregated researcher responses to questions linked to 1) definitions of reproducibility, 2) familiarity with and 3) use of reproducible research practices, and 4) potential barriers to reproducibility.

\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition of the term.
We coded these definitions following two procedures.
First, we measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
To create an aggregate measure of agreement the final coded response for each participant was then summed across the four characteristics, creating definition similarity \textit{d} with domain [0, 4].

Second, we coded each definition to one of three motivations for ensuring the reproducibility of a study--- to facilitate the assessment of prior work, to improve transparency and facilitate further extension of work, and to improve the transparency and consistency of study data.
We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

\textit{Familiarity and Experience:} We measured participant familiarity and use of five reproduciblity enhancing research practices; the adoption of--- open-source software, research notebooks, data sharing, code sharing, and research plan preregistration. 
We created a summary measure of familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
To assess experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
Both \textit{f} and \textit{p} have domains [0,5].

\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 factors contributed to a lack of reproducibility in the discipline. 
From those responses, we created a summary measure, \textit{b} with domain [0,12], of the number of barriers a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility.

Our second analysis examined only researchers that reported attempting a reproduction in the past two years. 
We asked each of these researchers what motivated their reproduction attempt. 
Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching. 
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and iv) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly well balanced across the disciplinary subfields - human geography (30.7\%), physical geography (29.8\%), nature and society (10.1\%), geographic methods and GIScience (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Perspectives on Reproducibility}
A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests a great deal of uncertainty about the true value. 
Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).

Table \ref{tab:overview} summarizes how researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of reproducible research practices (\textit{u}), and the factors they see as barriers (\textit{b}) to reproducibility in geography. 
We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
In aggregate, the data reveal trends in definition, familiarity, practices, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between sub-disciplines and methodological approaches.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of \textit{$n_{d}$}=181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
On average, geographic researchers provided definitions of reproducibility that explicitly included one or two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
This level of inclusion was consistent across subfields and methodological approaches.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods focused researchers.
The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data. 
For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."
We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so others could independently expand upon past studies.
Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample (\textit{n}=218). 
A majority of researchers identified reproducibility as important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
In parallel with the need for openness and transparency in science, most respondents agreed with the importance of reproducibility for research efficiency (63.3\%), communication with academics (68.8\%) and practitioners (64.7\%), and training students (75.7\%).

Despite wide recognition of reproducibility as epistemically important, respondents were cautious about drawing conclusions from a single study or reproduction attempt. 
Half of the respondents (50.9\%) agreed that when researchers don't share their data they have less trust in a study.
A similar percentage (41.7\%) agreed that inability to reproduce a result detracts from the validity of a study, and a smaller minority agreed that such inability implies that the result is false (26.2\%).

Qualitative researchers identified reproducibility as playing a much smaller epistemic role compared to the discipline as a whole. 
A majority of the qualitative researchers responded that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
Accordingly a small percentage of qualitative researchers agreed that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of research.
Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and expansion of research.
Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important for sharing research with academics (27.5\%).

>>>>

\begin{abstract}
While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility, the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have kept geographers from conducting more reproduction studies.
This study addresses each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
In contrast, many researchers did report attempting to reproduce their own work but not publishing those efforts, which suggests a foundation exists for the examination and expansion of reproducibility in the field.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
Nonetheless, reviews of published research papers reveal a lack of data and code for reproducibility \citep{moraila2014measuring, iqbal2016reproducible} and attempts to reproduce published research papers frequently fail \citep[see][]{raghupathi2022reproducibility, chang2015economics}.
Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
At the same time, a sizable portion of researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.

Many of these same factors may be impacting the reproducibility of geographic research, but they have yet to be systematically measured.
The small number of reproduction studies available within the discipline suggest that most studies are missing the components needed to attempt a reproduction; and of the studies with the needed components, many cannot be fully reproduced \citep[see][]{Kedron2022dimaggio, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
The available surveys of research practices in the discipline also support this conclusion as few researchers report sharing their data, metadata, or source code \citep{balz2020reproducibility, konkol2019, ostermann2017}.
At the same time, recent reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.

Despite these suggestive findings, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
This knowledge gap exists because researchers conducting reproducibility assessments have not defined clear target populations or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}. 
For example, reproductions of geographic research have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2022} or on specific topics such as COVID-19 \citep{Holler2023disability, kedron2021GA, paez2022reproducibility}.

More broadly, attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
These samples of researcher surveys and research papers have been convenient, but are not guaranteed to be representative of researchers and research activity in a particular field through random sampling. 
Like attempts to reproduce specific studies, reproducibility surveys have also focused on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use. 
The few available surveys of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017} face these same challenges.

Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}. 
And yet, we still have not systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies. 
Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research using a probability sampling scheme designed to capture the breadth of geographic research.
In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work. 
Finally, we discuss the implications of our survey results and conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
The OSF repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
We encourage interested readers to critically evaluate and build on these materials through their own work.
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

\subsection*{Survey Instrument}
The survey first established eligibility based on age and geographic research activity in the past five years and asked researchers to report their primary subfield and methodology.
We asked each participant to assess their familiarity with the term ``reproducibility'' and to provide their own definition. 
We then provided a definition based on the \citet{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
For researchers who reported attempting reproductions, we asked researcher to elaborate on their motivations and outcomes (9 questions).

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature. 
We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
Participation in the survey was entirely voluntary. 
Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium (self-identifying reference removed).

@@

%%%%%%%
\subsubsection*{Analyzing Researcher Perspectives on Reproducibility}
\noindent We conducted two statistical analyses of the survey responses.
First, we created descriptive statistical summaries of the participant response to assess how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.

\textit{Definition:} 
We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 4].

Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study--- (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.

\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproducibility enhancing research practices: the adoption of open-source software, research notebooks, data sharing, code sharing, and research plan preregistration. 
We created a measure of familiarity by counting the variety of practices a researcher was 'somewhat' or 'very' familiar with.
We measured experience by counting the variety of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
Both measures have domains [0, 5].

\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].

To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups. 
We then compared response frequencies cross subgroups.

%%%%%%%
\subsubsection*{Analyzing Researcher Reproduction Attempts}
\noindent Our second analysis examined only the responses of researchers that reported attempting a reproduction in the past two years to understand what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.

\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and/or increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching. 
We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
We selected groups i) and iv) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.

\textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study. 
We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants ability to access key study artifacts (e.g., data, procedural information, code).

Given the topical and epistemological variation that exists among geographic researchers, we again used cross-tabulation to examine differences in response by disciplinary subfield and methodological approach.
However, the size of our sub-sample for this analysis limited number of cross-tabulations we could pursue.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were academics, and they were balanced across career levels from graduate students to full professors as no one career level made up more that 30 percent of the sample.
Respondents were balanced across the disciplinary subfields--- physical geography (29.8\%), geographic methods and GIScience (28.0\%), nature and society (10.1\%), and human geography (30.7\%); and methodological approaches---quantitative (42.2\%), mixed methods (39.0\%), and qualitative (18.3\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Perspectives on Reproducibility}
Reproducibility is on the minds of geographic researchers.
Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%), with half reporting being very familiar with the term (53.6\%).
More pointedly, the majority of survey respondents reported thinking about the reproducibility of their own research (80.7\%), discussing reproducibility with a colleague (70.6\%), and questioning the reproducibility of published work (57.3\%) in the past two years. 
More than half of the researchers we surveyed (52.8\%) also reported considering reproducibility while peer reviewing a grant proposal or publication during the same time frame. 
However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests a great deal of uncertainty about the true value. 
Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%). 
Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in the discipline (58.2\%).

Table \ref{tab:overview} summarizes how researchers define reproducibility, their familiarity with reproducible research practices and experience using them, and the factors they see as barriers to reproducibility in geography. 
We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
In aggregate, the data reveal trends in definition, familiarity, experience, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between sub-disciplines and methodological approaches.

@@

%%%%%%%%%%%
\subsubsection*{Definitions and Importance of Reproducibility}
A total of 181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
This level of inclusion was consistent across subfields and methodological approaches.
The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods focused researchers.
The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data. 
For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."
We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.

Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
These ranged from rigid bitwise quantitative interpretations, as in the "ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which "other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results".
Responses included definitions with a focus on experimental science, as in "an ability to produce consistent results when an experiment is repeated!"

Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so that others could independently expand upon past studies.
For example a quantitative geographers stated: "The methods should provide sufficient information to be able to reproduce the results. In quantitative science this should, at minimum, provide all the equations and algorithms used for any calculation. In the interest of increasing transparency in science, the practice of sharing the code should be encouraged.
For others, open science did not necessarily need to result in identical results: "As a qualitative researcher doing in-depth case study research, my studies can not be perfectly reproduced. But reproducibility sits in the openness about methods and data collection practices, as well as critical reflection about strengths and weaknesses of my research. When we write about those things in the methods section in our papers and theses, their reproducibility is increased." 
The remainder of responses (6.6\%) emphasized repeatable and/or reliable data observation over all other dimensions of reproducibility.
For example, "As a historical geographer, working with qualitative research methods, I understand reproducibility more in terms of sources than of methods. I see reproducible research as being that which makes clear the origin and location of its data."
A physical geographer similarly emphasized data observations: "Data/observations of some variable can be recovered repeatedly by different observers/methods"
